Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-10 cmsb22.tex
Update model names

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns \(n\) and \(s\) denote the numbers of nodes (resp.\ input nodes) of each model. Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    ``DNF'' means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & \(n\) & \(s\) & \(|M|\) & PyBoolNet (s) & Trappist (s) \\
    \midrule
    InflammatoryBowelDisease & 47 & 0 & 1 & DNF & 21.90\\
    TLGLSurvival & 61 & 7 & 318 & 0.73 & 0.14\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 & 13 & 1000+ & 0.59 & 0.13\\
    Colitis\_associated\_colon\_cancer & 70 & 1 & 10 & 0.16 & 0.08\\
    mast\_cell\_activation\_model\_BCC & 73 & 19 & 1000+ & 0.64 & 0.15\\
    IL\_6\_Signalling & 86 & 15 & 1000+ & 3.30 & 0.10\\
    Corral\_ThIL17diff\_15jan2021 & 92 & 16 & 1000+ & DNF & 0.38\\
    korkut\_2015a & 99 & 12 & 1000+ & DNF & 0.61\\
    INTERFERON-1 & 121 & 55 & 1000+ & 8.36 & 0.19\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 & 4 & 78 & 40.81 & 0.33\\
    TCR-TLR5-SIGNALING-2018 & 130 & 5 & 48 & 0.88 & 0.12\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 & 11 & 1000+ & 63.62 & 0.21\\
    SIGNALING-IN-PROSTATE-CANCER & 133 & 11 & 1000+ & DNF & 0.32\\
    HIV-1 & 138 & 14 & 1000+ & DNF & 0.87\\
    FIBROBLASTS & 139 & 9 & 1000+ & DNF & 0.56\\
    HMOX1-PATHWAY & 145 & 56 & 1000+ & 5.16 & 0.18\\
    Kynurenine\_Pathway\_stable & 150 & 72 & 1000+ & DNF & 0.74\\
    VIRUS-REPLICATION-CYCLE & 154 & 25 & 1000+ & DNF & 0.19\\
    IMMUNE-SYSTEM & 164 & 13 & 1000+ & DNF & 0.67\\
    RA\_apoptosis\_executable\_module\_BCC & 180 & 59 & 1000+ & DNF & 0.16\\
    MAPK\_model\_BCC & 181 & 37 & 1000+ & 68.62 & 0.64\\
    ER-STRESS & 182 & 75 & 1000+ & 28.65 & 0.21\\
    CASCADE3 & 183 & 1 & 0 & 92.75 &  0.65\\
    cho\_2016\_all\_pos & 200 & 13 & 1000+ & DNF & 1.01\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 & 14 & 1000+ & 37.40 & 0.35\\
    ERBB-RECEPTOR-SIGNALING & 247 & 22 & 1000+ & DNF & 1.07\\
    Signaling\_in\_Macrophage\_Activation & 321 & 19 & 1000+ & 15.82 & 0.63\\
    cholocystokinin\_model\_BCC & 383 & 74 & 1000+ & 1.22 & 0.73\\
    Alzheimer\_model\_BCC & 762 & 237 & 1000+ & DNF & 1.03\\
    S1\_Table & 1659 & 521 & 1000+ & DNF & 44.85\\
    Human\_network & 1953 & 669 & 1000+ & DNF & 42.97\\
    SN5 & 2746 & 829 & ??? & DNF & DNF\\
    turei\_2016 & 4691 & 1257 & ??? & DNF & DNF\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns \(n\) and \(s\) denote the numbers of nodes (resp.\ input nodes) of each model. Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    ``DNF'' means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & \(n\) & \(s\) & \(|M|\) & PyBoolNet (s) & Trappist (s) \\
    \midrule
    inflammatory-bowel-disease & 47 & 0 & 1 & DNF & 21.90\\
    T-LGL-survival-network-2008 & 61 & 7 & 318 & 0.73 & 0.14\\
    butanol-production & 66 & 13 & 1000+ & 0.59 & 0.13\\
    colitis-associated-colon-cancer & 70 & 1 & 10 & 0.16 & 0.08\\
    mast-cell-activation & 73 & 19 & 1000+ & 0.64 & 0.15\\
    IL-6-signalling & 86 & 15 & 1000+ & 3.30 & 0.10\\
    Corral-ThIL-17-diff & 92 & 16 & 1000+ & DNF & 0.38\\
    Korkut-2015 & 99 & 12 & 1000+ & DNF & 0.61\\
    adhesion-cip-migration-cell-cycle & 121 & 4 & 78 & 40.81 & 0.33\\
    interferon-1 & 121 & 55 & 1000+ & 8.36 & 0.19\\
    TCR-TLR5-signaling-2018 & 130 & 5 & 48 & 0.88 & 0.12\\
    influenza-virus-replication-cycle & 131 & 11 & 1000+ & 63.62 & 0.21\\
    signaling-in-prostate-cancer & 133 & 11 & 1000+ & DNF & 0.32\\
    HIV-1-with-T-cell-signaling & 138 & 14 & 1000+ & DNF & 0.87\\
    signal-transduction-in-fibroblasts & 139 & 9 & 1000+ & DNF & 0.56\\
    HMOX-1-pathway & 145 & 56 & 1000+ & 5.16 & 0.18\\
    kynurenine-pathway & 150 & 72 & 1000+ & DNF & 0.74\\
    virus-replication-cycle & 154 & 25 & 1000+ & DNF & 0.19\\
    immune-system & 164 & 13 & 1000+ & DNF & 0.67\\
    RA-apoptosis & 180 & 59 & 1000+ & DNF & 0.16\\
    MAPK & 181 & 37 & 1000+ & 68.62 & 0.64\\
    er-stress & 182 & 75 & 1000+ & 28.65 & 0.21\\
    cascade-3 & 183 & 0 & 1 & 92.75 &  0.65\\
    CHO-2016 & 200 & 13 & 1000+ & DNF & 1.01\\
    T-cell-check-point & 218 & 14 & 1000+ & 37.40 & 0.35\\
    ErbB-receptor-signaling & 247 & 22 & 1000+ & DNF & 1.07\\
    signaling-macrophage-activation & 321 & 19 & 1000+ & 15.82 & 0.63\\
    cholocystokinin & 383 & 74 & 1000+ & 1.22 & 0.73\\
    Alzheimer & 762 & 237 & 1000+ & DNF & 1.03\\
    KEGG-network & 1659 & 521 & 1000+ & DNF & 44.85\\
    human-network & 1953 & 669 & 1000+ & DNF & 42.97\\
    SN-5 & 2746 & 829 & ??? & DNF & DNF\\
    turei-2016 & 4691 & 1257 & ??? & DNF & DNF\\
    \bottomrule
  \end{tabular}
\end{table}
